---
title: "Hurricane Hugo Impact on Concentration in Puerto Rico's Streams"
format: html
---

## Background 
This repository purpose is to reproduce figure 3 from Schaefer et al. (2000), that demonstrated the changes in stream chemistry overtime including hurricane disturbance by Huricane Hugo. The analysis focus on concentration changes in (a) potassium, (b) nitrate-N, (c) magnesium, (d) calcium and (e) ammonium-N in Bisley bason and Rio Mameyes Punete Roto.

## Data
Raw data was downloaded from the Environmental Data Initiative. https://doi.org/10.6073/pasta/f31349bebdc304f758718f4798d25458. 
  
  McDowell, W. and International Institute of Tropical Forestry(IITF), USDA Forest Service.. 2024. Chemistry of stream water from the Luquillo Mountains ver 4923064.


```{r}
#| warning: false

library(tidyverse)
```


## Methods
Cleaned data was developed by applying moving-average() and tidy-data() functions. The tidy_data function filters all the data from 1988-1994 and selects the ions needed for analysis. The moving-average 

Used a 9 week moving average 
```{r}
#| warning: false

```

## Results
```{r}
#| warning: false

```