---
title: "Hurricane Hugo Impact on Concentration in Puerto Rico's Streams"
format: html
---

## Background 
This repository purpose is to reproduce figure 3 from Schaefer et al. (2000), that demonstrated the changes in stream chemistry overtime including hurricane disturbance by Huricane Hugo. The analysis focus on concentration changes in (a) potassium, (b) nitrate-N, (c) magnesium, (d) calcium and (e) ammonium-N in Bisley bason and Rio Mameyes Punete Roto.

## Data
```{r}

library(tidyverse)

PRM_data <- read_csv("../data/RioMameyesPuenteRoto.csv")
bq1_data <- read_csv("../data/QuebradaCuenca1-Bisley.csv")
bq2_data <- read_csv("../data/QuebradaCuenca2-Bisley.csv")
bq3_data <- read_csv("../data/QuebradaCuenca3-Bisley.csv")
```


## Methods
```{r}
source("../R/moving-average.R")

PRM_moving <- moving_average(PRM_data)

PRM_moving |>
  pivot_longer(
    cols = c(k_mgl, mg_mgl, no3_ugl, ca_mgl, nh4_ugl),
    values_to = "Concentration",
    names_to = "Ion"
  ) |>
  ggplot(
    mapping = aes(x = window_start, y = Concentration, color = Ion)
  ) +
  geom_line() +
  facet_wrap(~Ion)
```

## Results
```{r}

```